From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-30 Pi+/paper/ufin.tex
More in UFin

@@

We lift these equivalences to $\UFin$ giving it the (additive) symmetric monoidal structure $(I, \oplus)$, with natural
isomorphisms $\lambda_{X}$, $\rho_{X}$, $\alpha_{X,Y,Z}$, and the symmetry isomorphism $\mathcal{B}_{X,Y}$. Note that
types in $\UFin$ are $\hSet$s since they're merely equivalent to $\Fin[n]$ for some $n : \Nat$.

>>>>

\[
  \begin{tikzcd}
    F_{0}
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=4em, in=115, out=65]
    & F_{1}
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=4em, in=115, out=65]
    & F_{2}
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=4em, in=115, out=65]
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=8em, in=125, out=55]
    & \ldots
    & F_{n}
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=4em, in=115, out=65]
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=8em, in=125, out=55]
    \arrow[""{anchor=center, inner sep=0}, no head, loop, distance=12em, in=135, out=45]
    & \ldots
  \end{tikzcd}
\]

@@

\begin{proposition}
  For any $n, m : \Nat$,
  \begin{align*}
    \Fin[1]                & \eqv \top        \\
    \Fin[n] \times \Fin[m] & \eqv \Fin[n * m] \\
  \end{align*}
  and for any types $X, Y, Z$,
  \begin{align*}
    \top \times X         & \eqv X                                \\
    X \times \top         & \eqv X                                \\
    (X \times Y) \times Z & \eqv X \times (Y \times Z)            \\
    X \times Y            & \eqv Y \times X                       \\
    X \times \bot         & \eqv \bot                             \\
    X \times (Y \sqcup Z) & \eqv (X \times Y) \sqcup (X \times Z)
  \end{align*}
\end{proposition}

We lift these equivalences to $\UFin$ giving it the additive and multiplicative symmetric monoidal structures,
$(O, \oplus)$ and $(I, \otimes)$, with corresponding natural isomorphisms $\lambda_{X}$, $\rho_{X}$, $\alpha_{X,Y,Z}$,
and the symmetry isomorphism $\mathcal{B}_{X,Y}$. Note that types in $\UFin$ are $\hSet$s since they're merely
equivalent to $\Fin[n]$ for some $n : \Nat$.

\todo{combine both symmetric monoidal structures}
